---
title: "Weight of Fish"
author: "April Parry"
date: "7/24/2023"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(car)
require(leaps)
```

# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```


### Best Two regressor model

 The two regression models are height and width. 

```{r}
Perchmodel <-lm(Weight~Height+Width, data=Perch)
summary.lm(Perchmodel)
```

from the data above it shows that the adjusted r-squared is 0.94 and the residual standard error is 85.17, also with a p-value of 2.2

## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```

From the data shown we can say that L1, L3 are the best two regression models.

### Best Models

```{r}
Pikebest <-lm(Weight~.,data=Pike)
summary.lm(Pikebest)
```

From the data The r-squared is 0.9794 and the residual error is 70.86. Then The p-value is 8.679. which shows that this is the best model


### Best Two regressor model

```{r}
Piketwo <-lm(Weight~Length1+Length3, data=Pike)
summary.lm(Piketwo)
```

 From the data above it shows that the  residual standard error is 92.56. The r-squared is 0.9649 and the p-value is 2.572e-11. and because the p-value is the smallest it shows the best results. 

## Roach

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")
summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

From all the data's The two best regression models is L1, L3.

### Best Models

```{r}
Roachrock <-lm(Weight~.,data=Roach)
summary.lm(Roachrock)
```

The residual standard error is 37.58. The r-squared is 0.821 and the p-value is 1.028e-05. From looking at this model it holds the smallest p-value out of all the models we did so far above.


### Best Two regressor model

```{r}
Roachbest <-lm(Weight~Length1+Length3, data=Roach)
summary.lm(Roachbest)
```

The residual standard error is 36.83. The r-squared is 0.8281 and the p-value is at 1.23e-07. From the data above This model holds the second to smallest p-value out of all the charts and models we have doned so far.


## Final Summary Statements

In conclusion the models above had created a data for us to compare and showed how different each model results can be . And so far The best models are L1 and L3. But all of them are equivalent to one another, since the results showed that they are all the best. Although  one of the models had The smallest p-value  which was the Roachrock model of 1.028e-05. 
